---
title: "THEMATICS - tabs - Eamon Madden"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/eamonmadden-sketch/Homework-2", align: right }

---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

Airbnb price map in Oakland CA. By Eamon Madden, using data from insideairbnb.com and oaklandca.gov. According to the spatial interpolation m I should charge 152 USD per night based on the Knn method, 141 from the IDW method, 142 from the nearest method, and 160 from the radius 1000 method

## Column {.tabset .tabset-fade}



```{r}
map1link ='https://github.com/eamonmadden-sketch/Homework-2/raw/refs/heads/main/RDS%20Outputs/Airbnb_Locations.rds'
viz1=url(map1link)

map2link ='https://github.com/eamonmadden-sketch/Homework-2/raw/refs/heads/main/RDS%20Outputs/Knn.rds'
viz2=url(map2link)

map3link ='https://github.com/eamonmadden-sketch/Homework-2/raw/refs/heads/main/RDS%20Outputs/IDW.rds'
viz3=url(map3link)

map4link = 'https://github.com/eamonmadden-sketch/Homework-2/raw/refs/heads/main/RDS%20Outputs/nearest.rds'
viz4=url(map4link)

map5link = 'https://github.com/eamonmadden-sketch/Homework-2/raw/refs/heads/main/RDS%20Outputs/radius_1000.rds'
viz5=url(map5link)
```

### Airbnb Locations

```{r}
readRDS(viz1)
```

### Calculating price with KNN method 

```{r}
readRDS(viz2)
```

### Calculating price with IDW method

```{r}
readRDS(viz3)
```

### Calculating price with nearest method

```{r}
readRDS(viz4)
```

### Calculating price with radius 1000 method

```{r}
map5 <- readRDS(viz5)
print(map5)
```




